\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2018-10-12 bare_conf.tex
some text editing.

% User interface
User interface consists of a wearable forehead belt, integrating RGB and depth cameras, inertial measurement unit (IMU), tactile feedback device and bone conduction headphones. Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people. Additionally, tactile actuators may improve the quality of users perception (e.g. by indicating the direction of detected object with vibromotor in the corresponding direction on the forehead, instead of providing longer and less convenient to perceive text-to-speach description of the event). UI can interface smartphone component via USB or Wifi connection.

% External vision processor
%visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
Although modern high-end smartphones contain quite powerful computers inside, many computer vision algorithms often demand hardware of significantly higher computational capacity (e.g. server with graphics processing unit (GPU)). This motivates us to employ external server for vision data processing. In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, \cite{Verilook}, obstacle detection \cite{Laina}, among others. After completing the analysis it's results are transmitted back to the smartphone component and represented to the user through the aforementioned interface.

@@

In this article we outlined an idea of complex computer vision-based cybernetic sensor architecture, which may help to partially compensate impaired or lost human sight. Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection, present the output of video processing to the user through a combined audio/tactile interface. Comparing to an existing commercial products e.g. \cite{orcam}, \cite{horus}, our approach is advantageous, since it does not rely only on computational capacity of mobile handset. Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of mobile networks to 5G. Combined audio/tactile interface also may be more convenient for the users, since it allows to provide more concentrated information comparing to purely audio or purely tactile interface.

@@

\bibitem{orcam} https://www.orcam.com/en/

>>>>

% User interface
User interface consists of a wearable forehead belt, integrating RGB and depth cameras, inertial measurement unit (IMU), tactile feedback device and bone conduction headphones. Although more expensive than standard ones, bone conduction headphones do not block the ears and allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people. Additionally, tactile actuators may improve the quality of users perception (e.g. by indicating the direction of detected object with vibromotor in the corresponding area on the forehead belt, instead of providing longer and less convenient to perceive audio description of the event). UI can interface smartphone component via USB or Wifi connection.

% External vision processor
%visus sutrumpinimus reikia pirma parasyt pilnai, pvz Neural Network (NN)
Although modern high-end smartphones are quite powerful computers themselves, many computer vision algorithms often demand hardware of significantly higher computational capacity (e.g. server with graphics processing unit (GPU)). This motivates us to employ external server for vision data processing. In our design we assume such a server with a set of computer vision algorithms implemented and exposed via web services: faster regions with convolutional neural network features (faster R-CNN) object detector \cite{Ren}, trained to detect important objects, convolutional and recurrent neural network (CNN and RNN)-based scene description \cite{Liu}, which provides textual annotation of a given RGB image, place recognition \cite{Ohn-Bar}, face detection and recognition \cite{Amos}, \cite{Verilook}, obstacle detection \cite{Laina}, among others. After completing the analysis it's results are transmitted back to the smartphone component and represented to the user through the aforementioned interface.

@@

In this article we outlined an idea of computer vision-based cybernetic sensor architecture, which may help to partially compensate impaired or lost human sight. Main advantages of therein suggested system are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via the Internet connection, present the output of video processing to the user through a combined audio/tactile interface. Comparing to an existing commercial products e.g. \cite{orcam}, \cite{horus}, our approach is advantageous, since it does not rely only on computational capacity of mobile handset. Such a combination of mobile interface and remote vision processor will be even more efficient in the future, with switching of mobile networks to 5G. Combined audio/tactile interface also may be more convenient for the users, since it allows to provide more concentrated information comparing to purely audio or purely tactile interface.

@@

\bibitem{orcam} https://www.orcam.com
